paper1_results_figs_slimmed_50

### 2016-03-23 pap1_figs_slimmed_50_unequal.Rmd
copied from paper1_figures_slimmed50.Rmd to enable looking at new unequal scenarios

## TRIAL VERSION OF ALL FIGS AT 50% resistance threshold

## Main Figures for paper 1 : version 5 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed_50.Rmd

@@

  ## to load previously saved runs
#   load(file=paste0(outFolder,'listOutMix_1000.rda'))
#   load(file=paste0(outFolder,'listOutI1_1000.rda'))
#   load(file=paste0(outFolder,'listOutI2_1000.rda'))

  ## trying with the extended experiment _ex100
  experiment <- 'extended'

  load(file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  load(file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

  # load(file=paste0(outFolder,'listOutMix_ex2_1000.rda'))
  # load(file=paste0(outFolder,'listOutI1_ex2_1000.rda'))
  # load(file=paste0(outFolder,'listOutI2_ex2_1000.rda'))

@@

@@

>>>>

## ALL FIGS AT 50% resistance threshold

## Main Figures for paper 1 : version 6 - in progress
### This file is automagically generated by R from paper1_results_figs_slimmed_50.Rmd

@@

  ## to load previously saved runs

  ## trying with the extended experiment
  experiment <- 'extended'

  # load(file=paste0(outFolder,'listOutMix_ex2_10000.rda'))
  # load(file=paste0(outFolder,'listOutI1_ex2_10000.rda'))
  # load(file=paste0(outFolder,'listOutI2_ex2_10000.rda'))

  load(file=paste0(outFolder,'listOutMix_unequal.rda'))
  load(file=paste0(outFolder,'listOutI1_unequal.rda'))
  load(file=paste0(outFolder,'listOutI2_unequal.rda'))

@@

  #BEWARE eval set to fale becuase new unequal runs caused an error in this chunk

@@

## Fig. x8 Introducing a new insecticide when there is already resistance to an existing one. This takes Curtis Fig 2 and sets the starting frequency for each allele in turn to a higher level to represent an 'old' insecticide to which there is resistance. In both cases resistance to the new insecticide develops slower when the 'old' insecticide continues to be used (mixture) than when it doesn't (sequence).

#curtis_f2 with P_1 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.49 , P_2 = 0.01 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43, addCombinedStrategy=FALSE )

#curtis_f2 with P_2 changed from 0.01 to 0.45 : mix slower than seq
runcurtis_f2( P_1 = 0.01 , P_2 = 0.49 , h.RS1_A0 = 0.17 , h.RS2_0B = 0.0016 , exposure = 0.9 , phi.SS1_A0 = 0.73 , phi.SS2_0B = 1 , s.RR1_A0 = 0.23 , s.RR2_0B = 0.43, addCombinedStrategy=FALSE )
